---
title: "COVID-19 Nursing Home Data"
output: 
  flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}
# load packages

#### TEST GITHUB CLONE



```



Interactive model & GITHUB TEST
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}
# shiny inputs defined here

# US state

selectInput("state", label = strong("State:"),
            choices = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", "VT", "VA", "WA", "WV", "WI", "WY"), selected = "AL"
           )

# slider for week



# PPE shortage

checkboxGroupInput("ppe", label = strong("Reported PPE shortage?:"),
    c("No" = 0, "Yes" = 1), selected = "No"
)


# size of facility

selectInput("facility_size", label = strong("Size of facility (# occupied beds):"), 
            choices = c("Small (0-100 beds)", "Large (100+ beds)"))



```
 
Column
-------------------------------------
    
### Predicted total resident and staff deaths for the month of December
    
```{r}


```

Column
-------------------------------------
    
### Probability of reporting a PPE shortage
    
```{r}


```


About this dataset
=======================================================================

### **Summary of the public health problem: COVID in nursing homes**

### **Data source**

These data come from the **CMS COVID-19 public use files**, which were reported weekly starting in May 2020. These data are self-reported by nursing homes and capture variables that include resident COVID deaths, resident COVID infections, staff COVID deaths, staff COVID infections, whether or not facilities had adequate PPE and COVID tests, and other descriptive variables. 

### **Data caveats**

+ As is always the case with self-reported facility data, **response bias** ...
+ 

Variable info
=======================================================================



Model info
=======================================================================

### Motivation/aim

The purpose of this model is to estimate the **total number of nursing home resident deaths in the month of December** for different states, varied by inputs that include  **facility-reported PPE shortages** and **size of nursing home facilities (large or small) based on number of occupied beds.**  

This information is of interest for public health planning and policy because **[rationale]**. 

### Model details

These data are fitted with a 


### Model caveats

