---
title: "COVID-19 Nursing Home Data"
output: 
  flexdashboard::flex_dashboard
runtime: shiny
---

```{r global, include=FALSE}
# load packages





```



Interactive model 
=======================================================================

Inputs {.sidebar}
-------------------------------------

```{r}
# shiny inputs defined here

# US state


selectInput("state", label = strong("State:"),
            choices = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", "VT", "VA", "WA", "WV", "WI", "WY"), selected = "AL"
           )

# slider for week


# size of facility

selectInput("facility_size", label = strong("Size of facility (# occupied beds):"), 
            choices = c("small (0-100 beds)", "large (100+ beds)"))

# PPE shortage

radioButtons("ppe_shortage", label = strong("Reported PPE shortage?:"),
    c("Yes" = 1, "No" = 0), selected = 1
)


```
 
Column
-------------------------------------
    
### **Predicted probability of a facility-reported staffing shortage**
    
```{r}



```

Column
-------------------------------------
    
### **Interpretation** 
    
```{r}


```

For a **`r renderText(input$facility_size)`** nursing home facility in **`r renderText(input$state)`**, there was a XXXX probability of the facility reporting a staffing shortage at least once in the time period from XXXX based upon this model. 

Motivation/aim
=======================================================================

### **Summary of the public health problem: COVID in nursing homes**



### **Purpose of model**

The purpose of this model is to estimate the **likelihood of a nursing home facility reporting a staffing shortage** for different states, varied by inputs that include  **facility-reported PPE shortages,** **size of nursing home facilities (large or small) based on number of occupied beds**, and **staff and resident cases**.  

### **Policy relevance** 

This information is of interest for public health planning and policy because it begins to provide a clearer picture of where facility-reported staffing shortages were most acute during this phase of the pandemic. This information could be used for several planning purposes: 

1) It could indicate where additional federal resources should be directed to understaffed and under-resourced nursing homes;
2) It could be useful in vaccine rollout planning as strategies to vaccinate nursing home staff are developed; and 
3) It could elucidate characteristics of facilities that might require additional staffing and other types of assistance for planning purposes in future pandemics.





About this dataset
=======================================================================

### **Data source**

These data come from the **CMS COVID-19 public use files**, which were reported weekly starting in May 2020. These data are self-reported by nursing homes and capture variables that include resident COVID deaths, resident COVID infections, staff COVID deaths, staff COVID infections, whether or not facilities had adequate PPE and COVID tests, and other descriptive variables. 

### **Data caveats**

+ As is always the case with self-reported facility data, **response bias** ...
+ Collection of COVID nursing home data has been a fraught endeavor throughout the pandemic - the CMS reporting sought to harmonize data definitions in this dataset, but a thoughtful summary of these many data problems can be found at the COVID tracking project webpage. 

### **References**

+ McGarry et al., Health Affairs
+ COVID Tracking Project: Data in Long-term Care Facilities
+ AARP: COVID in Nursing homes 



Model details
=======================================================================

### **Model & equation **

These data are fitted with a **logistic regression model**. This model was selected because a binary outcome is of interest.

Pr()

### **Model caveats**

Additional models would also be appropriate to explore in this situation given that the data are time-varying and that some of the outcomes being discussed here are relatively rare events. 

Variable info
=======================================================================
**Outcome variable:** 

+ Reported staff shortage: Any reported staff shortage from the time period XXXX. 


**Predictor variables:**

+ PPE shortage
+ Cumulative # resident cases  
+ Cumulative # staff cases
+ Size of facility

